---
title: "Assignment2"
author: "Salem Malibary"
date: "2024-09-19"
output: html_document
editor_options: 
  chunk_output_type: console
---

```{r setup, include=TRUE}
knitr::opts_chunk$set(echo = TRUE)
# This chunk has all the resources needed to create the report. These are the included packages which needed to conduct the report
library(tidyverse)
library(haven)
library(labelled)
library(knitr)
library(tibble)

# This is the original dataset which has all the variables and observations
data <- haven::read_sav("data.sav")

```

---

# Methods

## Dataset Description

The information for this study named "Reactions of Financial Professionals to Workaholism in Nigeria" was sourced from the Harvard Dataverse - a reliable and openly available database, for research information - which is a public data repository.The dataset contains feedback from a survey conducted across Nigeria involving employees in the industry.

The survey explore into work habits such as workaholism and investigates facets of employee well-being,career satisfaction and relationships within the workplace hierarchy. 

The dataset falls into the business and management category. Includes various important factors essential for comprehending workaholic behaviors. The dataset includes various essential variables, such as "**working excessively**", "**working compulsively**", "**career prospects**", "**leader-member exchange**", and "cynicism".

The variables in this dataset are essential for comprehending "**workaholic behaviors**", "**employee satisfaction**", and "**leadership dynamics**". This data holds relevance for studying the elements that influence the "**affect employee well-being and organizational relationships**".

## Data Reading &  Cleaning:

We inspected the dataset for any missing values across all variables to ensure completeness. No missing values were found, so no imputation or removal was necessary.

#### Overview of the variables and observation of the dataset

```{r Overview of the variables and observation of the dataset}
dplyr::glimpse(data)
```



#### Original questions used to collect the data

```{r Original labels used to collect the data}
labelled::var_label(data)
```

```{r, echo=FALSE}
var_labels <- 
  tibble::tibble(
  Variable = c("WE1", "WE2", "WE3", "WE4", "WE5","WC1", "WC2","WC3","WC4","WC5","CP1", "CP2", "CP3", "CP4", "CP5","LMX1","LMX2","LMX3","LMX4","LMX5","LMX6","LMX7","CY1","CY2","CY3","CY4","CY5","CY6","Age","Tenure","EdQual","Gender","SUMWE","SUMWC","SUMCP","SUMLMX","SUMCY","AgeGrp","TenGrp"),
  Label = c(
    "I always seem to find myself to be in a hurry and racing against the clock.",
    "I find myself continuing to work after my coworkers have called it quits.",
    "I stay busy and engaged in too many activities at the same time.",
    "I spend more time working than on socializing with friends, on hobbies, or on leisure activities.",
    "I find myself doing two or three things at one time such as eating lunch and writing a memo.",
    "It is important to me to work hard even when I do not enjoy what I am doing.",
    "I feel that there is something inside me that drives me to work hard.",
    "I feel obliged to work hard, even when it is not enjoyable.",
    "I feel guilty when I take time off work.",
    "It is hard for me to relax when I am not working.",
    "I am satisfied with the success I have achieved in my career.",
    "I am satisfied with the progress I have made toward meeting my overall career goals.",
    "I am satisfied with the progress I have made toward meeting my goals for income.",
    "I am satisfied with the progress I have made toward meeting my goals for advancement.",
    "I am satisfied with the progress I have made toward meeting my goals for the development of new skills.",
    "I am usually satisfied with what my leader does.",
    "My leader has a good understanding of my job problems and needs.",
    "My boss/leader recognizes my potentials.",
    "Do you think that there are chances that your leader would use his/her power to help you solve problems in your work?",
    "Are there chances that your leader would bail you out at his/her expense?",
    "I have enough confidence in my leader that I would defend and justify his/her decision if he/she were not present to do so.",
    "I have a very good working relationship with my leader.",
    "I do NOT think my organization is sincere.",
    "I am NOT taken seriously in this organization.",
    "Most times I laugh it off when my organization pushes me to the wall.",
    "I withhold suggestions at times because I know my office would do nothing about it.",
    "I usually talk to my colleagues about management’s incompetence.",
    "There are times I shrug my shoulders at what Management requires me to do.",
    "Age of respondents.",
    "Length of time spent at the organization.",
    "Educational qualification of respondents.",
    "Gender of respondents.",
    "Sum of working excessively items.",
    "Sum of working compulsively items.",
    "Sum of career prospects items.",
    "Sum of Leader-Member-Exchange items.",
    "Sum of cynicism items.",
    "Group data on age range.",
    "Group data on tenure range."
  )
)
knitr::kable(var_labels, 
             caption = "Variable and Original Labels")
```

#### Retreive the original catogorical observation's answers

```{r To understand the observation of each variable}
# This function is repeated every time a variable is used in the study but for convenient just written one time
data |> 
  dplyr::select(CY4) |> 
  dplyr::distinct()
```


## Statistical Methods

---

# Results

## Descriptive Statistics

## Correlation Analysis

## Visualizations

---

# Discussion

## Interpretation of Results

## Implications

## Limitations

## Future Research

---

# Conclusion